How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference

### 2018-03-19 paper/paper_entailVis.tex
adjust evaluation panel size

% \documentclass[journal]{vgtc}                % final (journal style)
\documentclass[review,journal]{vgtc}         % review (journal style)
%\documentclass[widereview]{vgtc}             % wide-spaced review
%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)

@@

%% it is recomended to use ``\autoref{sec:bla}'' instead of ``Fig.~\ref{sec:bla}''
\graphicspath{{figures/}{pictures/}{images/}{./}} % where to search for the images

@@

%% declare the category of your paper, only shown in review mode
\vgtccategory{Research}
%% please declare the paper type of your paper to help reviewers, only shown in review mode
%% choices:
%% * algorithm/technique
%% * application/design study
%% * evaluation
%% * system
%% * theory/model
\vgtcpapertype{please specify}

%% Paper title.
\title{Where and Why Do Models Fail?  A Visualization Tool for Analyzing and Interpreting Natural Language Inference}

%% This is how authors are specified in the journal style

@@

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }

@@

%% the only exception to this rule is the \firstsection command
\input{intro.tex}
\input{relatedWorks.tex}
\input{background.tex}
% \input{tasks.tex}
\input{perturbation.tex} % how to do the perturbation
\input{attention.tex} % how to encode the information
\input{application.tex}
%%%%%%%%%%%%% identify errors %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% interpret attention %%%%%%%%%%%%%%%%%%%

>>>>

% \documentclass[journal]{vgtc}                % final (journal style)
\documentclass[review,journal]{vgtc}         % review (journal style)
% \documentclass[review,journal]{vgtc}         % review (journal style)
%\documentclass[widereview]{vgtc}             % wide-spaced review
%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)

@@

%% it is recomended to use ``\autoref{sec:bla}'' instead of ``Fig.~\ref{sec:bla}''
\graphicspath{{figures/}{pictures/}{figs/}{./}} % where to search for the images

@@

%% declare the category of your paper, only shown in review mode
\vgtccategory{Research}
%% please declare the paper type of your paper to help reviewers, only shown in review mode
%% choices:
%% * algorithm/technique
%% * application/design study
%% * evaluation
%% * system
%% * theory/model
\vgtcpapertype{application}

%% Paper title.
\title{How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference}
%% This is how authors are specified in the journal style

@@

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }
\teaser{
% \vspace{-8mm}
 % \includegraphics[width=0.78\linewidth]{teaser}
 \includegraphics[width=.96\linewidth]{teaser.pdf}
 \centering
 % \vspace{-3mm}
  \caption{
 System overview.
  }
\label{fig:teaser}
}

@@

%% the only exception to this rule is the \firstsection command
\input{intro.tex}
\input{relatedWorks.tex}
\input{background.tex}
% \input{tasks.tex}
\input{perturbation.tex} % how to do the perturbation
\input{attention.tex} % how to encode the information
\input{pipeline.tex}
\input{application.tex}
%%%%%%%%%%%%% identify errors %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% interpret attention %%%%%%%%%%%%%%%%%%%
